Spin canonical rings of log stacky curves

### 2015-07-09 surfaces-write-up/surface-write-up.tex
added lattice generation proposition

@@

\begin{example}
\label{eg:radical}
As an example for why we need to add in ghost points for $\bp^2$, consider $\frac{-1}{5}V(x_0^2) + \frac{1}{7}V(x_1^2) + \frac{1}{17}V(x_2^2)$. In degree $595 = 5* 7 * 17$, this has dimension $6$, but we cannot possibly use the lattice approach, as all lower degrees only have dimension 1. In fact, we may construct similar examples using any $x_i^m$ for $f_i$ with appropriate coefficients.
\end{example}
\todo{construct class of additional examples}

>>>>

\section{Lemmas for Generation and Relations}

\begin{prop}
\label{prop:cone-generation}
Let $n,t \in \bz,$ let $\alpha_1, \ldots, \alpha_n \in \bq$ and let $k_i^j \in \bz$ with $1 \leq i \leq n, 1 \leq j \leq t.$ Define
\begin{align*}
	\Sigma = \{(d,c_1, \ldots, c_n) \in \bz^{n+1} : c_i \geq - d \alpha_i,1 \leq i \leq n \text{ and } \sum_{i=1}^{n}k_i^j = 0, 1 \leq j \leq t\}
\end{align*}
Let $e_1, \ldots, e_r \in \Sigma,$ with $e_i = (\delta^i, c_1^i, \ldots, c_n^i)$ be a set of {\bf extremal rays} of $\Sigma$, meaning that the $\Sigma$ is contained in the $R_{\geq 0}$ span of $e_1, \ldots, e_n$.  Then, as a semigroup, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
\end{prop}
\begin{proof}
By assumption, $\sigma \in \Sigma$ as $\sigma = \sum_{i=1}^{n}a_i e_i$ with $a_i \in \br$. Let $\{a\} := a - \lfloor a \rfloor$ denote the fractional part of $a$. Let $\lambda = \sum_{i=1}^{n}\{a_i\}$. Hence, we can write $\sigma = \lambda + \sum_{i=1}^{n}\lfloor a_i \rfloor e_i.$ Hence, $\sigma$ lies in the $\bz_{\geq 0}$ span of $\lambda, e_1,\ldots, e_n$, which all have first coordinate less than $\sum_{i=1}^{n}\delta_i$. Therefore, $\Sigma$ is generated by elements whose first coordinate is less than $\sum_{i=1}^{n}\delta_i$.
\end{proof}

@@

\begin{example}
\label{eg:radical}
As an example for why we need to add in ghost points for $\bp^2$, consider $\frac{-1}{5}V(x_0^2) + \frac{1}{7}V(x_1^2) + \frac{1}{17}V(x_2^2)$. In degree $595 = 5* 7 * 17$, this has dimension $6$, but we cannot possibly use the lattice approach, as all lower degrees only have dimension 1. In fact, we may construct similar examples using any $x_i^m$ for $f_i$ with appropriate coefficients.
\end{example}
\todo{construct class of additional examples}
\todo{The example above needs to be changed because $x_0^2$ can be replaced by $2x_0$}
